### 2017-07-01 UOW_thesis_template_v2-0/thesis_template/chapters/Intro.tex
Fixed up last corrections given by Marianito

	A well-known result for determining the option value is known as the Black-Scholes formula \cite{Black1973}. The Black-Scholes formula is in fact a partial differential equation (PDE) that is also paired with a terminal condition governed by a payoff function. The payoff function merely states what the option's value will be at the expiry date. Typically, this is normally some linear function of the strike price and the underlying asset (at least in terms of a call and put). One of the most classical methods to solve the Black-Scholes PDE system is to invoke a transformation of variables (further details of this in addition to~\cite{Black1973} can be found in~\cite{Wilmott1995}) that effectively eliminates a few terms and reduces the PDE system to the archetypal heat equation commonly seen in thermodynamics~\cite{cannon1984one}. The motivation for this step is because the heat equation has been studied endlessly in literature and the solution to the PDE system is ascertainable~\cite{Churchill1938}. The original details of~\cite{Black1973} can also be complemented with~\cite{Wilmott1995} for further details and discussion about this derivation. The crux of option valuation is to determine a fair price for the holder to pay the writer to enter into their specified contract. This price is commonly known as the \emph{option premium} (or simply, the premium) that actually signifies the value of the option at time-zero (i.e., starting today).

@@

Another class of methods to price American-type derivatives are analytical approximations that account for both the derivative value itself and any embedded features (e.g., American options and the early exercise premium). The most notable technique was proposed by Barone-Adesi and Whaley~\cite{Barone1987} where they developed a quadratic approximation method that replaces the early exercise premium with a term that is quadratic in the underlying asset (with all attached quantities to be either known or able to be determined using known values). Undoubtedly, this would prove beneficial in terms of minimising computational effort and their simulation results prove that the accuracy is also comparable to the FDM and the compound option approach of Geske.

@@

For non-compound options, a recent extension was provided by Bos and  Wandermark~\cite{Bos2002} that splits the multiple dividends into two categories: ``near'' (dividend payments about to occur) and ``far'' (dividend payments close to expiry). The rationale used was to subtract the ``near'' dividends from the underlying's value and add ''far" dividends to the strike price. This was an attempt to reconcile methods by Hull~\cite[pp. 298]{Hull1989} and Musiela and Rutkowsky~\cite[pp. 53--54]{Musiela1997}. The former simply subtracted the total value of all dividends in the option's lifetime from the current underlying asset's price. Once this adjustment is made, the option price can be determined. The latter method accumulates the total value of all dividends paid during the lifetime of the option and appends this as a scaling factor to the value of the underlying asset at expiry. From there, one works backwards in time to calculate the option's value. The latter method also assumed the dynamics of the underlying asset to be governed by the Cox-Ross-Rubinstein model~\cite{Cox1979}. Veiga and Wystup~\cite{Veiga2009} notably developed a closed form option pricing formula for assets paying discrete dividends. The formula is expressed in terms of the standard European call option plus a truncated series involving the dividend and derivatives of the aforementioned call (which are obtained by using a Taylor series approximation). The cited works~\cite{Roll1977},~\cite{Geske1979},~\cite{Bos2002}, and~\cite{Veiga2009} formulated the stochastic differential equation (SDE) that models the underlying asset to account for the dividend payment(s) as a term which signifies a cash dividend of a fixed size. This total value of the dividend is not contingent on the value of the underlying asset post-dividend payment date. This distinction between a yield and a cash payment is crucial when constructing the mathematical model to price the underlying asset.

>>>>

	A well-known result for determining the option value is known as the Black-Scholes formula \cite{Black1973}. The Black-Scholes formula is in fact a partial differential equation (PDE) that is also paired with a terminal condition governed by a payoff function. The payoff function merely states what the option's value will be at the expiry date. Typically, this is normally a piecewise linear function of the strike price and the underlying asset (at least in terms of a call and put). One of the most classical methods to solve the Black-Scholes PDE system is to invoke a transformation of variables (further details of this in addition to~\cite{Black1973} can be found in~\cite{Wilmott1995}) that effectively eliminates a few terms and reduces the PDE system to the archetypal heat equation commonly seen in thermodynamics~\cite{cannon1984one}. The motivation for this step is because the heat equation has been studied endlessly in literature and the solution to the PDE system is ascertainable~\cite{Churchill1938}. The original details of~\cite{Black1973} can also be complemented with~\cite{Wilmott1995} for further details and discussion about this derivation. The crux of option valuation is to determine a fair price for the holder to pay the writer to enter into their specified contract. This price is commonly known as the \emph{option premium} (or simply, the premium) that actually signifies the value of the option at time-zero (i.e., starting today).

@@

Another class of methods to price American-type derivatives are analytical approximations that account for both the derivative value itself and any embedded features (e.g., American options and the early exercise premium). The most notable technique was proposed by Barone-Adesi and Whaley~\cite{Barone1987} where they developed a quadratic approximation method that replaces the early exercise premium with a term that is quadratic in the underlying asset (with all attached quantities to be either known or able to be determined using known values). Undoubtedly, this would prove beneficial in terms of minimising computational effort and their simulation results prove that the accuracy is also comparable to the finite difference method (FDM) and the compound option approach of Geske.

@@

For non-compound options, a recent extension was provided by Bos and  Wandermark~\cite{Bos2002} that splits the multiple dividends into two categories: ``near'' (dividend payments about to occur) and ``far'' (dividend payments close to expiry). The rationale used was to subtract the ``near'' dividends from the underlying's value and add ``far'' dividends to the strike price. This was an attempt to reconcile methods by Hull~\cite[pp. 298]{Hull1989} and Musiela and Rutkowsky~\cite[pp. 53--54]{Musiela1997}. The former simply subtracted the total value of all dividends in the option's lifetime from the current underlying asset's price. Once this adjustment is made, the option price can be determined. The latter method accumulates the total value of all dividends paid during the lifetime of the option and appends this as a scaling factor to the value of the underlying asset at expiry. From there, one works backwards in time to calculate the option's value. The latter method also assumed the dynamics of the underlying asset to be governed by the Cox-Ross-Rubinstein model~\cite{Cox1979}. Veiga and Wystup~\cite{Veiga2009} notably developed a closed form option pricing formula for assets paying discrete dividends. The formula is expressed in terms of the standard European call option plus a truncated series involving the dividend and derivatives of the aforementioned call (which are obtained by using a Taylor series approximation). The cited works~\cite{Roll1977},~\cite{Geske1979},~\cite{Bos2002}, and~\cite{Veiga2009} formulated the stochastic differential equation (SDE) that models the underlying asset to account for the dividend payment(s) as a term which signifies a cash dividend of a fixed size. This total value of the dividend is not contingent on the value of the underlying asset post-dividend payment date. This distinction between a yield and a cash payment is crucial when constructing the mathematical model to price the underlying asset.

### 2017-07-01 UOW_thesis_template_v2-0/thesis_template/chapters/jumpdiffEuro.tex
Fixed up last corrections given by Marianito

There is also interest in finding an exact solution for Kou's double exponentially distributed jumps \cite{Kou2002, Kou2004} using \eqref{eqn:optionJump} and \eqref{eqn:jumpGeneral} since recent empirical studies suggest a better model for the asset process involves the jumps following a double exponential distribution. In particular, it may be of interest to see whether or not a Mellin transform route would generate a more elegant and simple solution in lieu of Kou's original solution, which involves the computation of quite complicated $Hh$ functions (see \cite[pp. 691]{Abramowitz1972}). There is also the possibility to extend \eqref{eqn:optionJump} to price American options in jump-diffusion models; this is current work in progress.

>>>>

There is also interest in finding an exact solution for Kou's double exponentially distributed jumps \cite{Kou2002, Kou2004} using \eqref{eqn:optionJump} and \eqref{eqn:jumpGeneral} since recent empirical studies suggest a better model for the asset process involves the jumps following a double exponential distribution. In particular, it may be of interest to see whether or not a Mellin transform route would generate a more elegant and simple solution in lieu of Kou's original solution, which involves the computation of quite complicated $Hh$ functions (see \cite[pp. 691]{Abramowitz1972}). There is also the possibility to extend \eqref{eqn:optionJump} to price American options in jump-diffusion models, which will be examined in chapter 5 of this thesis.
